On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/experiments.tex
experiments

We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}. We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{The code of models along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}. For training we have used NVIDIA's GeForce GTX TITAN X. We followed the implementation details indicated in the original paper~\cite{hudson2018compositional} (Section A of the supplementary material), to ensure a faithful comparison.

@@

We report the obtained scores in \tableref{results}. Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31h of training.\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data. As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}. 
The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score. Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of ~10\% in wall time. This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.

>>>>

We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}. We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{Code along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}. For training we have used NVIDIA's GeForce GTX TITAN X. We followed the implementation details indicated in supplemental (Sec. A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.

@@

We report the obtained scores in \tableref{results}. Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31h of training.\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data. As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}. \tk{not sure why we report this, is it state-of-the-art?}
The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score. Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of ~10\% in wall time. This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.
